---
title: "TrichomeDualDefense Figs"
output: html_document
date: "2023-05-12"
---

```{r Load package}
library(ggplot2)
```

``````{r Correlations}
#Correlations with herbicide resistance
p1<- ggplot(T2, aes(x=BranchedPer, y=HerbRes1)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE) + theme_classic(base_size = 20) + ylab("Herbicide Resistance") + ylim(0,0.75) + xlab("Proportion Branched Trichomes")   

p2 <- ggplot(T2, aes(x=CapitatePer, y=HerbRes1)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE, linetype = "dashed") + theme_classic(base_size = 20) + ylab("Herbicide Resistance") + ylim(0,0.75) + xlim(0,0.21)+ xlab("Proportion Capitate Trichomes") 

p3 <- ggplot(T2, aes(x=Density, y=HerbRes1)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE, linetype = "dashed") + theme_classic(base_size = 20) + ylab("Herbicide Resistance") + ylim(0,0.75) + xlab("Total Trichome Density")

#Correlations with herbivory resistance
p4 <- ggplot(T0_2, aes(x=BranchedPer, y=Herbivory)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE) + theme_classic(base_size = 20) + ylab("Herbivory Resistance") + xlab("Proportion Branched Trichomes") 

p5 <- ggplot(T0_2, aes(x=CapitatePer, y=Herbivory)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE, linetype = "dashed") + theme_classic(base_size = 20) + ylab("Herbivory Resistance") + xlab("Proportion Capitate Trichomes") 

p6 <- ggplot(T0_2, aes(x=Density, y=Herbivory)) +
  geom_point(alpha = 0.3,  size = 4, position = position_jitter()) + stat_smooth(method = "lm", size = 1.5, color = "black", se=FALSE,  fullrange = TRUE, linetype = "dashed") + theme_classic(base_size = 20) + ylab("Herbivory Resistance") + xlab("Total Trichome Density") 

#Combine graphs

p1 + p4/ p2+p5 / p3 +p6
```

```{r Fitness}
#Fitness

ggplot(T0_2, aes(x=DensityResStand, y=RelFitness, color = TRT, linetype = TRT)) +
  geom_point(alpha = 1,  size = 3, position = position_jitter()) + geom_smooth(method = "lm", size = 1, se=FALSE,  fullrange = TRUE) + theme_classic(base_size = 18) + ylab("Relative Fitness") + xlab("Total Trichome Density") + scale_color_manual(values = c("black", "grey")) + scale_linetype_manual(values=c( "solid", "dashed")) + ylim(0,8)

ggplot(T0_2, aes(x=BranchedResStand, y=RelFitness, color = TRT, linetype = TRT)) +
  geom_point(alpha = 1,  size = 3, position = position_jitter()) + geom_smooth(method = "lm", size = 1, se=FALSE,  fullrange = TRUE) + theme_classic(base_size = 18) + ylab("Relative Fitness") + xlab("Proportion Branched Trichomes") + scale_color_manual(values = c("black", "grey")) + scale_linetype_manual(values=c("solid", "solid")) + ylim(0,8)

ggplot(T0_2, aes(x=CapitateResStand, y=RelFitness, color = TRT)) +
  geom_point(alpha = 1,  size = 3, position = position_jitter()) + stat_smooth(method = "lm", size = 1, se=FALSE,  fullrange = TRUE, linetype = "dashed") + theme_classic(base_size = 18) + ylab("Relative Fitness") + xlab("Proportion Capitate Trichomes") + scale_color_manual(values = c("black", "grey")) + ylim(0,8)
```
```
